Capon Beamforming Applied on Moving Objects - An Analysis of Local Lateral Shift-Invariance

### 2013-11-16 HRUIofMovingObjects/jrnl_article.tex
Moving objects article: doen some writing

@@

>>>>

Phase rotation will introduced block artifacts equal to the once observed when using PRB. This can be improved on by implementing a phase rotation version of STB where 8PR are converted to 4PR-STB by averaging 4 phase rotated outputs from two beams rotated to the same angle.

@@

Other methods claiming super resolution would also need some degree of oversampling (Eigenspace, LCA etc.).

When oversampling is applied (L=M/2, K=1, d=1/100) becomes too extreme. L=M/4 with K=0 is better.

Oversampling is not only essential to keep the amplitude level of bright point scatterers it will also help to improve contrast and edge definitions. If oversampling is not applied the edge delineation of an moving object will fluctuate in the same way as a moving point scatterer.
